Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-23 paper.tex
Corrections

In the context of both deadlines and dependencies coupled with packet loss, partial reliability
requires application-level framing \cite{clark:1990:architecture} to
make the best use of payload data. At the transport
layer, this implies a \emph{message oriented} service, that
maintains application data unit (ADU) boundaries. Messages are delivered to
the application in the order they arrive. For example, the combination of
reliability and in-order delivery in TCP can introduce significant latency:
incoming segments may be head-of-line blocked waiting for the delivery of
an earlier segment.

@@

At the intermediary layer on the receiver, incoming segments are scanned
for complete messages (i.e., data between two zero bytes), which are
decoded and passed to the application. While the segments are sent
containing only one message, these may be resegmented or coalesced in the
network. A segment may arrive containing \emph{fragments} of message
data. These fragments are buffered, alongside their TCP sequence number, 
awaiting the arrival of the remainder of the message. Once the message has
been reassembled, it is decoded, and delivered to the application.
% TCP Hollywood inherits standard TCP's congestion control mechanism.
% Clearly, being a loss-based algorithm, this is not appropriate for
% real-time applications.
% \todo{discuss how we need to change TCP congestion control}

>>>>

In the context of both deadlines and dependencies coupled with packet loss, partial reliability
requires application-level framing \cite{clark:1990:architecture} to
make the best use of payload data. At the transport
layer, this implies a \emph{message oriented} service, that
maintains application data unit (ADU) boundaries. Messages are delivered to
the application in the order they arrive. As seen in TCP, in-order delivery
can introduce significant latency: incoming segments may be head-of-line
blocked waiting for the delivery of an earlier segment.

@@

At the intermediary layer on the receiver, incoming segments are scanned
for complete messages (i.e., data between two zero bytes), which are
decoded and passed to the application. While segments are sent
containing only one message, these may be resegmented or coalesced in the
network. A segment may arrive containing \emph{fragments} of message
data. These fragments are buffered, alongside their TCP sequence number, 
awaiting the arrival of the remainder of the message. Once the message has
been reassembled, it is decoded, and delivered to the application.
% TCP Hollywood inherits standard TCP's congestion control mechanism.
% Clearly, being a loss-based algorithm, this is not appropriate for
% real-time applications.
% \todo{discuss how we need to change TCP congestion control}
